SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-07-25 scipy-1.0/paper.tex
Add a short section on maintainers and contributors.

\textbf{Maintainers and contributors}

>>>>

\textbf{Maintainers and contributors}
The SciPy project has approximately 15 active maintainers (people who review
others' contributions, and in general do everything needed to ensure that
the software and the project move forward).  It also has an additional ~100
unique contributors for every 6-monthly release cycle.  Maintainers are
critical to the health of the project\cite{eghbal2016}; they enable contributions
from a much larger group, and their skills and efforts largely determine how
fast the project moves forward.  Anyone with the interest and skills can become
a maintainer; the SciPy Developer Guide provides guidance on how to do that.
